### 2017-11-15 Draft2/Indexing.Growth.tex
Rename labels
Work
Bogus citation

Indexing a growth array is slower and more complex than indexing a dynamic array. However, this does not mean that accessing data of a growth array is necessarily slower than accessing that of a dynamic array. Refer to Sections \ref{sec:Iterating} and \ref{sec:CopyArray} for methods to quickly access growth arrays' data.

@@

% Todo: cite.
To see this, first note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$. There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss because it involves concepts outside the scope of this paper. Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.

>>>>

Indexing a growth array is slower and more complex than indexing a dynamic array. However, this does not mean that accessing data of a growth array is necessarily slower than accessing that of a dynamic array. Refer to Sections \ref{subsec:Iterating} and \ref{subsec:ConvertRawArray} for methods to quickly access growth arrays' data.

@@

To see this, first note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$. There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss because it involves concepts outside the scope of this paper \cite{ceillog2}. Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.
